\documentclass[12pt, oneside,english,hidelinks,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc} % Allows UTF-8 input
\usepackage{amsmath} % For advanced math typesetting
\usepackage{graphicx} % For including images
\usepackage{hyperref} % For hyperlinks
\usepackage{geometry} % For customizing page dimensions
\geometry{a4paper, margin=1in} % Set paper size and margins

% Document
\title{Your Article Title}
\author{Your Name}
\date{\today} % Use \today for today's date or a specific date

\begin{document}

\maketitle % Generates title, author, and date

\begin{abstract}
% 300 WORDS
% 984 characters
This bachelor thesis focuses on analysing and evaluating recommender systems best suitable for digital library datasets. With the rise of digital content, these systems help users navigate large information spaces by generating personalized recommendations. In the introduction we showed the importance and role of Recommender Systems (RS) in filtering and anticipating user preferences across various domains. We then described the different recommendation techniques in detail, showing how they work and what their difficulties are. The project emphasizes Content-Based Filtering techniques, comparing algorithms like BERT, Word2Vec, LDA, and TF-IDF. Offline experiments tested the system’s ability to provide Top-N book recommendations from the input data and the algorithms were compared based on evaluation metrics such as Usage Prediction, Coverage, Diversity, and Confidence. This work aims to evaluate different recommendation algorithms designed for digital library datasets.
\end{abstract}

\section{Introduction}
This section introduces the topic of your article. Provide background information and state the objectives or purpose of your work.

\section{Main Content}
\subsection{Subsection 1}
This is the first subsection of your main content. Add details, arguments, and any relevant content here.

\subsection{Subsection 2}
This is another subsection. Include further information and elaborate on your ideas.

\section{Conclusion}
Summarize the key points discussed in the article. Highlight the significance of your work and suggest future directions, if applicable.





\clearpage 
\normalsize 
\bibliographystyle{unsrt} 
\bibliography{article_literature} 
\nocite{*}

\end{document}
